Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-08-06 drafts/outline.tex
might have lost some changes from Overleaf?
Updates from Overleaf

Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}). Effective capture efficiency ($\eta^\prime=p_r\eta=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation. This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.

@@

\begin{figure}[htbp]
TODO
\centering
\caption{flume floorplan}
\label{fig:floorplan}
\end{figure}

>>>>

Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}). Effective capture efficiency ($\eta^\prime=p_r\eta$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation. This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.

@@

\begin{figure}[htbp]
TODO
\centering
\caption{Conceptual diagram of the laboratory flume}
\label{fig:floorplan}
\end{figure}
